Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-14 paper/paper.qmd
Updated areas of improvement

The dataset used in the paper was compiled in 2018 and we currently do not know if any of the homicide cases have been solved as of 2024 and how many, which limits the years we were able to analyze. There are other factors like the resources of the police department that could have also impacted the outcome of homicides being unsolved, which we did not have information on and that could have reduced the accuracy of our model. Since some information in the dataset was aggregated by humans from not only FBI data but also papers, human error could have occur when inputting information into the data. For future works on unsolved homicides, we recommend compiling a new dataset for the years 2018 to 2024 similar to what The Washington Post did and considering other factors like the resources of the police departments [@datahomicides].

>>>>

The dataset used in the paper was compiled in 2018 and we currently do not know which homicide cases have been solved as of 2024, which limits the years we were able to analyze. There are other factors like the resources of the police department that could have also impacted the outcome of homicides being unsolved, which we did not have information on and that could have reduced the accuracy of our model. Since some information in the dataset was aggregated by humans from not only FBI data but also papers, human error could have occur when inputting information into the data. For future works on unsolved homicides, we recommend compiling a new dataset for the years 2018 to 2024 similar to what The Washington Post did and considering other factors like the resources of the police departments [@datahomicides].
